---
title: "R Notebook"
output: html_notebook
---
```{r}
library(ggplot2)
data <- read.csv("./data.csv")
print(data)
ggplot(data,aes(x=start_at,y=close))+geom_line()
#keep <- c("open","high","low","close") 
#data <- data[keep]
head(data)

```


```{r}
######創建對應之y_label
shift <- function(x, n) {  
 c(x[-(seq(n))], rep(NA, n)) 
} 
data$shifted <- shift(data$close, 1) 
print(data) 
data <- na.omit(data) 
write.csv(data, "data_1.csv")


######標準化

normalize <- function(x) {
    return((x- min(x)) /(max(x)-min(x)))
}
data["close"] <- as.data.frame(apply(data["close"],2, normalize))
data["high"] <- as.data.frame(apply(data["high"],2, normalize))
data["open"] <- as.data.frame(apply(data["open"],2, normalize))
data["low"] <- as.data.frame(apply(data["low"],2, normalize))
data["shifted"] <- as.data.frame(apply(data["shifted"],2, normalize))

print(data)
ggplot(data,aes(x=start_at,y=shifted))+geom_line()

```


```{r}
#loading the library 
library(h2o) 
h2o.init(nthreads = -1, max_mem_size = "8g") 
```




```{r}
y <- "shifted" #variable we want to forecast 
x <- c("open","high","low","close")
l <- round(nrow(data)*0.8)
train <- data[c(1:l),]
test <- data[c(l+1:nrow(data)),]
train <- as.h2o(train)
test <- as.h2o(test)
qq <- as.data.frame(test)
ggplot(qq,aes(x=start_at,y=close))+geom_line()
print(train
      )
```



```{r}

automodel <- h2o.automl(x, y, train, test,sort_metric = "RMSE",nfolds = 4) 
```

```{r}
lb=h2o.get_leaderboard(object = automodel, extra_columns = "ALL")
print(lb)
predictions <- h2o.predict(automodel@leader, test)
```


```{r}
h2o.saveModel(automodel@leader,path="./GBM_nor_4f_nshuf")

```
```{r}
###denormalize
deno <- function(x,max,min) {
    return(x*(max-min)+min)
}
deno_truth <- read.csv("./data.csv")
deno_truth$shifted <- shift(deno_truth$close, 1) 
deno_truth <- na.omit(deno_truth)
print(max(deno_truth["close"]))
predictions <- deno(predictions,max(deno_truth["shifted"]),min(deno_truth["shifted"]))
print(predictions)
test["shifted"] <- deno(test["shifted"],max(deno_truth["shifted"]),min(deno_truth["shifted"]))
test["close"] <- deno(test["close"],max(deno_truth["close"]),min(deno_truth["close"]))
print(test["shifted"])
print(nrow(test))

#h2o.exportFile(predictions,path="./pred_nor.csv",force=TRUE)


```
```{r}

cal <- function(pred,truth){
  len <- nrow(pred)
  mae <- 0
  mse <- 0
  for(i in c(1:len)){
    mse <- mse+(pred[i]-truth[i])^2
    mae <- mae+abs(pred[i]-truth[i])
  }

  mse <- mse/len
  mae <- mae/len
  print(mae)
  print(mse)
  x <- mean(truth)
  rrdif <- 0
  rrt <- 0
  for(i in c(1:len)){
    rrdif <- rrdif+(pred[i]-truth[i])**2
    rrt <- rrt+(truth[i]-x)**2
  }
  y <- 1-rrdif/rrt
  print(y)
  
  return(c(mae,mse,y))
}
```
```{r}
s <- cal(array(predictions),array(test["shifted"]))
#print(test["shifted"])
#print(predictions[1])
print(cat("mae:",s[1]))
print(cat("mse:",s[2]))
print(cat("R2:",s[3]))
```


```{r}
print(nrow(test))
h2o.exportFile(predictions,path="./pred_nor_GBM.csv",force=TRUE)
h2o.exportFile(test,path="./truth_GBM.csv",force=TRUE)
```
```{r}
model_a=h2o.loadModel("./GBM_nor_4f/GBM_4_AutoML_1_20220108_130208")
pred <- h2o.predict(model_a, test)
deno <- function(x,max,min) {
    return(x*(max-min)+min)
}
deno_truth <- read.csv("./data.csv")
deno_truth$shifted <- shift(deno_truth$close, 1) 
deno_truth <- na.omit(deno_truth)
print(max(deno_truth["close"]))
predictions <- deno(predictions,max(deno_truth["shifted"]),min(deno_truth["shifted"]))
print(predictions)
test["shifted"] <- deno(test["shifted"],max(deno_truth["shifted"]),min(deno_truth["shifted"]))
s <- cal(array(pred),array(test["shifted"]))
```
```{r}
qq <- as.data.frame(test)
qq["pppp"] <- array(predictions)
ggplot(qq,aes(x=start_at,y=shifted))+geom_line()+ggplot(qq,aes(x=start_at,y=pppp))+geom_line()
kk <- as.data.frame(predictions)

```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
